`r params$doc_title`

### 2022-12-22 scripts/MSc.Rmd
arranged performance plots X,U,Y

# read dat from "simstudy.R"  #------------------------------------------------
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
```

@@

```{r simulated-pves, fig.height=6, fig.width=10, warning=FALSE}
# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

est_sim %>% 
  select(!!!(colname_pve_U)) %>% 
  pivot_longer(everything(), names_to = "PVE_U", values_to = "value_U") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_U_sim

est_sim %>% 
  select(!!!(colname_pve_Y)) %>% 
  pivot_longer(everything(), names_to = "PVE_Y", values_to = "value_Y") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_Y_sim

@@

# retrieve PVE colnames
colname_pve_X <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_X_sim")]
colname_pve_U <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_U_sim")]
colname_pve_Y <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_Y_sim")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GSD
colname_IVW_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GSD_")]
colname_IVW_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GSD_")]
colname_MODE_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GSD_")]
colname_MODE_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GSD_")]
colname_CONMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GSD_")]
colname_CONMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GSD_")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GBC
colname_IVW_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GBC_")]
colname_IVW_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GBC_")]
colname_MODE_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GBC_")]
colname_MODE_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GBC_")]
colname_CONMIX_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GBC_")]
colname_CONMIX_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GBC_")]

@@

```{r boxplot-theta-sim-distribution, fig.height=6, fig.width=10}
# compare distribution of simulated thetas against theta_324000
boxplot_dat <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = format(as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")), scientific=FALSE))

ggplot(boxplot_dat, aes(x=forcats::fct_rev( as.factor(theta_sim_numeric)), y=value)) +
  geom_boxplot()+
  geom_jitter(width=0.1,alpha=0.2)+
  geom_hline(yintercept=  args$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = "300000", y = args$theta+0.5,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
  scale_x_discrete(name = paste0("Size of sample ", as.roman(1)),  breaks = c(" 50000", "100000", "150000", "200000", "250000", "300000"), )+ 
  ylab(expression(paste(theta[sim], " with ", n[sim]== 25 ) )  ) +
  labs(title = "Estimates from beta simulation",
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       )+
  coord_flip()+
  theme_few() -> simplot_thetas
simplot_thetas

### same plot as above, but from already calculated performance metrics theta_mean + theta_sd
ggplot(performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 300000, y = args$theta+0.25,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error")+
  theme_few() -> simplot_thetas2
simplot_thetas2

filename_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_thetas.png")
ggsave(filename = filename_simplot_thetas, plot = simplot_thetas, 
       width = 10, height = 6, 
       units = "in"  # default
       )
filename_simplot_thetas2 <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_thetas2.png")
ggsave(filename = filename_simplot_thetas2, plot = simplot_thetas2, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

```{r plot-performance-metrics-bias-mse, fig.height=6, fig.width=14}
#BIAS
ggplot(performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "Bias with Empirical Standard Error")+
  theme_few() -> biasplot

#MSE
ggplot(performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "MSE")+
  theme_few() -> mseplot

ggarrange(biasplot, mseplot) ->bias_mse_plot
bias_mse_plot

filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_bias_mse.png")
ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot, 
       width = 14, height = 6, 
       units = "in"  # default
       )
```

>>>>

# read dat from "simstudy.R"  #------------------------------------------------
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

```{r simulated-pves, fig.height=6, fig.width=10, warning=FALSE}
# retrieve PVE colnames
colname_pve_X <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_X_sim")]
colname_pve_U <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_U_sim")]
colname_pve_Y <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_Y_sim")]

## for performance measures later
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GSD 
colname_IVW_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GSD_")]
colname_IVW_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GSD_")]
colname_MODE_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GSD_")]
colname_MODE_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GSD_")]
colname_CONMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GSD_")]
colname_CONMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GSD_")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GBC
colname_IVW_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GBC_")]
colname_IVW_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GBC_")]
colname_MODE_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GBC_")]
colname_MODE_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GBC_")]
colname_CONMIX_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GBC_")]
colname_CONMIX_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GBC_")]

# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim
# CONFOUNDER PVE
est_sim %>% 
  select(!!!(colname_pve_U)) %>% 
  pivot_longer(everything(), names_to = "PVE_U", values_to = "value_U") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_U_sim
# OUTCOME PVE
est_sim %>% 
  select(!!!(colname_pve_Y)) %>% 
  pivot_longer(everything(), names_to = "PVE_Y", values_to = "value_Y") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_Y_sim

@@

@@

### GSD simulated theta distribution

```{r theta-sim-distribution-GSD-old, eval=FALSE, fig.height=6, fig.width=10, include=FALSE}
### OLD
# # compare distribution of simulated thetas against theta_324000
# boxplot_dat <- est_sim %>% 
#   select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
#   pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
#   mutate(theta_sim_numeric = format(as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")), scientific=FALSE))
# 
# ggplot(boxplot_dat, aes(x=forcats::fct_rev( as.factor(theta_sim_numeric)), y=value)) +
#   geom_boxplot()+
#   geom_jitter(width=0.1,alpha=0.2)+
#   geom_hline(yintercept=  args.gsd.ivw$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
#   annotate(geom = "text", x = "300000", y = args$theta+0.5,
#            label= expression( paste("ref: ", theta[X] ))  , 
#            color= ggthemes_data$few$colors$Dark[9,2][[1]]
#              )+
#   scale_x_discrete(name = paste0("Size of sample ", as.roman(1)),  breaks = c(" 50000", "100000", "150000", "200000", "250000", "300000"), )+ 
#   ylab(expression(paste(theta[sim], " with ", n[sim]== 25 ) )  ) +
#   labs(title = "Estimates from beta simulation",
#        caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
#        )+
#   coord_flip()+
#   theme_few() -> simplot_thetas
# simplot_thetas
```

```{r theta-sim-distribution-GSD, fig.height=6, fig.width=10, warning=FALSE}
## IVW
IVW_BMI_GSD_geom_point_dat <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(IVW_GSD_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gsd.ivw$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gsd.ivw$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = IVW_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = IVW_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "IVW estimate: BMI -> GSD")+
  theme_few() -> IVW_GSD_simplot_thetas
IVW_GSD_simplot_thetas

## MODE
MODE_BMI_GSD_geom_point_dat <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(MODE_GSD_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gsd.mode$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gsd.mode$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = MODE_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = MODE_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "MODE estimate: BMI -> GSD")+
  theme_few() -> MODE_GSD_simplot_thetas
MODE_GSD_simplot_thetas

## CONMIX
CONMIX_BMI_GSD_geom_point_dat <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gsd.conmix$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gsd.conmix$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = CONMIX_BMI_GSD_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = CONMIX_BMI_GSD_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "CONMIX estimate: BMI -> GSD")+
  theme_few() -> CONMIX_GSD_simplot_thetas
CONMIX_GSD_simplot_thetas

# SAVE
filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
```
```{r theta-sim-distribution-GSD-arrange, fig.height=18, fig.width=10, warning=FALSE}
IVW_GSD_simplot_thetas$labels$title <- ""
MODE_GSD_simplot_thetas$labels$title <- ""
CONMIX_GSD_simplot_thetas$labels$title <- ""
ggarrange(IVW_GSD_simplot_thetas,MODE_GSD_simplot_thetas,CONMIX_GSD_simplot_thetas, 
          ncol = 1, nrow = 3) -> GSD_simplot_thetas_arrange

filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
       width = 10, height = 18, 
       units = "in"  # default
       )
```

### GSD Bias & MSE

```{r plot-performance-metrics-bias-mse-GSD, fig.height=10, fig.width=5}
## IVW
#BIAS
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> biasplot_IVW_GSD
#MSE
ggplot(IVW_GSD_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(0,1.8))+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "IVW estimate: BMI -> GSD")+
  theme_few() -> mseplot_IVW_GSD
ggarrange(biasplot_IVW_GSD, mseplot_IVW_GSD) -> bias_mse_plot_IVW_GSD

## MODE
ggplot(MODE_GSD_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "MODE estimate: BMI -> GSD")+
  theme_few() -> biasplot_MODE_GSD
ggplot(MODE_GSD_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
    geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(0,1.8))+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "MODE estimate: BMI -> GSD")+
  theme_few() -> mseplot_MODE_GSD
ggarrange(biasplot_MODE_GSD, mseplot_MODE_GSD) -> bias_mse_plot_MODE_GSD

## CONMIX
ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(-1.5,1.5))+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "CONMIX estimate: BMI -> GSD")+
  theme_few() -> biasplot_CONMIX_GSD
ggplot(CONMIX_GSD_performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  geom_hline(yintercept=  0, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  scale_x_continuous(labels = comma)+
  scale_y_continuous(limits = c(0,1.8))+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "CONMIX estimate: BMI -> GSD")+
  theme_few() -> mseplot_CONMIX_GSD
ggarrange(biasplot_CONMIX_GSD, mseplot_CONMIX_GSD) -> bias_mse_plot_CONMIX_GSD

ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD,
          ncol = 1, nrow = 3, common.legend = TRUE) -> bias_mse_plot_GSD
bias_mse_plot_GSD

filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_NSIM_", nsim, ".png")
ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
       width = 7, height = 10, 
       units = "in"  # default
       )
```

### GBC simulated theta distribution

```{r theta-sim-distribution-GBC, fig.height=6, fig.width=10, warning=FALSE}
## IVW
IVW_BMI_GBC_geom_point_dat <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GBC)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(IVW_GBC_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gbc.ivw$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gbc.ivw$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = IVW_BMI_GBC_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = IVW_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = IVW_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "IVW estimate: BMI -> GBC")+
  theme_few() -> IVW_GBC_simplot_thetas
IVW_GBC_simplot_thetas

## MODE
MODE_BMI_GBC_geom_point_dat <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GBC)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(MODE_GBC_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gbc.mode$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gbc.mode$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = MODE_BMI_GBC_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = MODE_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = MODE_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "MODE estimate: BMI -> GBC")+
  theme_few() -> MODE_GBC_simplot_thetas
MODE_GBC_simplot_thetas

## CONMIX
CONMIX_BMI_GBC_geom_point_dat <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GBC)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")))

ggplot(CONMIX_GBC_performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args.gbc.conmix$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 50000, y = args.gbc.conmix$theta+0.05,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  ## ADD rainbow plots
  geom_boxplot(data = CONMIX_BMI_GBC_geom_point_dat, aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2, outlier.shape = NA)+
  ggdist::stat_halfeye(data = CONMIX_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric, y=value, group=theta_sim_numeric), 
                       inherit.aes = FALSE, 
                       slab_fill=ggthemes_data$few$colors$Dark[3,2][[1]], slab_alpha = 0.2,
                       geom = "slabinterval",
                       na.rm=TRUE, trim=TRUE, adjust = .5, width = 10000, .width = 0, justification = -.3, point_colour = NA)+
  gghalves::geom_half_point(
    data = CONMIX_BMI_GBC_geom_point_dat, mapping=aes(x=theta_sim_numeric-2000, y=value, group=theta_sim_numeric), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[3,2][[1]],
    side = "l", range_scale = .4, alpha = .2)+
  ## FINISH rainbow
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error", subtitle = "CONMIX estimate: BMI -> GBC")+
  theme_few() -> CONMIX_GBC_simplot_thetas
CONMIX_GBC_simplot_thetas
